---
title: "Every City Canada Demo"
author: "Jens von Bergmann"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(tidyverse)
library(sf)
library(cancensus)
library(cancensusHelpers)
library(rtweet)
#devtools::install_github("tarakc02/rmapzen")
library(rmapzen)
library(ggalt)
library(grid)
library(gridExtra)
library(EveryCityCanada)
```

# How to use EveryCityCanada

As input we need a city as returned by cancensus *list_census_regions*.
```{r}
cities=cities_list()
city <- cities %>% sample_n(1)
```

# Plotting the city card
To get the plot for the city we call the *every_city_plot* function. Gathering the data and drawing the vector map can take a little bit of time.
```{r}
image_path=every_city_plot(city)
browseURL(image_path)
```

# Tweeting

To tweet out a random city use the *send_every_city_tweet* function. Optionally specify the city to send out a tweet for a specific city. 

```{r}
send_every_city_tweet(city)
```

